New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/schur.tex
tableaux section 3

Using a SAT solvers, we are able to exhibit SF-template,
hence providing lower bound on \(S^+\). Moreover, when using
a SF-template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(S^+(k+1)\). Further details can be found in the
\hyperref[SAT]{SAT section}.
Here are the best inequalities on Schur numbers so far :
\[ S(n+1) \geqslant 3S(n) + 1 \]
\[ S(n+2) \geqslant 9S(n) + 4 \]
\[ S(n+3) \geqslant 33S(n) + 6 \]
\[ S(n+4) \geqslant 111S(n) + 43 \]
\[ S(n+5) \geqslant 380S(n) + 148 \]
\[ S(n+6) \geqslant 1140S(n) + 528 \]

>>>>

Using a SAT solvers, we are able to exhibit SF-template, hence providing lower bound on \(S^+\). 
We seek templates providing the best lower bound possible, but also the best additive constant (\(m_{k+1}\) with the previous notation). 
Further details can be found in the\hyperref[SAT]{SAT section}. \\

Here are the best inequalities on Schur numbers so far :
\[ S(n+1) \geqslant 3S(n) + 1 \]
\[ S(n+2) \geqslant 9S(n) + 4 \]
\[ S(n+3) \geqslant 33S(n) + 6 \]
\[ S(n+4) \geqslant 111S(n) + 43 \]
\[ S(n+5) \geqslant 380S(n) + 148 \]
\[ S(n+6) \geqslant 1140S(n) + 528 \]
